### 2016-02-11 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Some minor things
Some minor fixes in captions etc.

The main contribution of the paper is to come up with an improved FRF by developing a method for smoothing the FRF estimated via the LPM. This is done by truncating the associated impulse response, as in \citep{Schoukens1998ImprFRFmeas}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the LPM for leakage reduction. The cutoff index (truncation point) is determined by a statistically sound method. It is then shown that a smooth LPM estimate of the FRF lowers the variance, thus improving the assessment level of the dynamic properties of a given LTI system.

Based on \citep{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an output-error (OE) framework. A single-input-single-output (SISO) LTI system is considered. %, based on  \citep{Schoukens2009LPM}. 
The input signal is a known random noise signal and the output signal is corrupted by measurement noise. This is depicted in Fig. 1 as a linear dynamic discrete-time SISO system, whose full mathematical model is of the form:
\begin{equation}\label{lpmtd1}
y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
\end{equation}
where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer). %\JL{$G_0(q)$ represents the dynamics of the system to be estimated.}

@@

Using convolution, the noiseless output signal in Fig. \ref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise. As shown in \citep{Pintelon2012} and \citep{Pintelon1997} the \gls{DFT} spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
\begin{equation}\label{lpmleak}
Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
\end{equation}
where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term. 
In this paper, the \gls{DFT} of a signal $x(t)$ is defined explicitly as  \citep{Oppenheim1983}

@@

The following assumptions are consistent with \citep{Schoukens2009LPM} for an OE setup (Fig. \ref{lpmtdrep}):
\begin{assumption}
The SISO system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
\end{assumption}

@@

The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
\TODO{ordos are incorrect: notation-wise}
\begin{align}\label{lpmGTaylorS}
G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
\\
\label{lpmTTaylorS}
T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
\\
\text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
\end{align}

@@

\begin{assumption}\label{ass:imprespdecay}
The impulse response $g(t)$ decays exponentially with time, i.e. $\exists A \in \PositiveRealNumbers, \exists a \in \NegativeRealNumbers \without \Set{0}, \forall t \in \PositiveRealNumbers: \abs{g(t)} \leq A \exp(- a t)$.
\end{assumption}

\begin{assumption}\label{ass:decay90perctime}
Within $90\%$ of the measurement window, the impulse response decays 
 to a level that is indistinguishable from the noise.

\end{assumption}

@@

\TODO{fix reference Section II}
Smoothing of the estimated \gls{FRF} requires the correct estimate of the impulse response. Unfortunately, the \gls{LPM} presented in \secref{se:theoryLPMandWindowing} and in \citep{Schoukens2009LPM} does not estimate the \gls{FRF}  at the frequency $\Omega_0$ (i.e. \gls{DC} value of the \gls{FRF}), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}. Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct. This anomaly is rectified by developing a simple estimator of the mean value, presented below.

\subsubsection{Estimating the \glsentrytext{DC} Value of the \glsentrytext{FRF}}\label{se:DCvalueEst}

The correct mean value of the impulse response accounts for (i.e. estimates) the \gls{DC} value of the \gls{FRF}. A time-domain method is proposed for estimating the mean value of the impulse response in equation \eqref{eq:impRespiDFT}. %The first is a frequency-domain technique and the second is a time-domain technique.

@@

The truncation time is determined from the data as described in Section \ref{se:truncImpulseResp}. This was done on $1000$ realizations of the noise, and depicted in Figure \ref{fig:pdfAndRMSeVStruncTime} by the histogram.
Clearly, the method for selecting the truncation time $t_{\mathrm{trunc}}$ has a good overall performance, based on the mode of its distribution. A closely grouped set of values for $t_{\mathrm{trunc}}$ is obtained around the $90^{\text{th}}$ sample, without significant outliers.

>>>>

The main contribution of the paper is to come up with an improved FRF by developing a method for smoothing the FRF estimated via the LPM. This is done by truncating the associated impulse response, as in~\citep{Schoukens1998}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the LPM for leakage reduction. The cutoff index (truncation point) is determined by a statistically sound method. It is then shown that a smooth LPM estimate of the FRF lowers the variance, thus improving the assessment level of the dynamic properties of a given LTI system.

Based on \citep{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an output-error (OE) framework. A single-input-single-output (SISO) LTI system is considered. %, based on  \citep{Schoukens2009LPM}.
The input signal is a known random noise signal and the output signal is corrupted by measurement noise. This is depicted in \figref{lpmtdrep} as a linear dynamic discrete-time SISO system, whose full mathematical model is of the form:
\begin{equation}\label{lpmtd1}
y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
\end{equation}
where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer). %\JL{$G_0(q)$ represents the dynamics of the system to be estimated.}

@@

Using convolution, the noiseless output signal in \figref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise. As shown in \citep{Pintelon2012} and \citep{Pintelon1997} the \gls{DFT} spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
\begin{equation}\label{lpmleak}
Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
\end{equation}
where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term.
In this paper, the \gls{DFT} of a signal $x(t)$ is defined explicitly as  \citep{Oppenheim1983}

@@

The following assumptions are consistent with \citep{Schoukens2009LPM} for an OE setup (\figref{lpmtdrep}):
\begin{assumption}
The SISO system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
\end{assumption}

@@

The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
\TODO{ordos are incorrect: notation-wise}
\begin{align}\label{lpmGTaylorS}
G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
\bigO{\left(\frac{r}{N}\right)^{(R+1)}},
\\
\label{lpmTTaylorS}
T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
\bigO{  \left(\frac{r}{N}\right)^{(R+1)}  }
,
\\
\text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
\end{align}

@@

\begin{assumption}\label{ass:imprespdecay}
The impulse response $g(t)$ decays exponentially over time, i.e. $\exists A \in \PositiveRealNumbers, \exists a \in \NegativeRealNumbers \without \Set{0}, \forall t \in \PositiveRealNumbers: \abs{g(t)} \leq A \exp(- a t)$.
\end{assumption}

\begin{assumption}\label{ass:decay90perctime}
Within $90\%$ of the measurement window, the impulse response decays
 to a level that is indistinguishable from the noise.
\end{assumption}

@@

\TODO{fix reference Section II}
Smoothing of the estimated \gls{FRF} requires the correct estimate of the impulse response. Unfortunately, the \gls{LPM} presented in \secref{se:theoryLPMandWindowing} and in \citep{Schoukens2009LPM} does not estimate the \gls{FRF}  at the frequency $\Omega_0$ (i.e. \gls{DC} value of the \gls{FRF}), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}. Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct. 
This limitation is lifted by developing a simple estimator of the mean value, presented below.

\subsubsection{Estimating the \glsentrytext{DC} Value of the \glsentrytext{FRF}}\label{se:DCvalueEst}
The correct mean value of the impulse response accounts for (i.e. estimates) the \gls{DC} value of the \gls{FRF}. A time-domain method is proposed for estimating the mean value of the impulse response in equation \eqref{eq:impRespiDFT}. %The first is a frequency-domain technique and the second is a time-domain technique.

@@

The truncation time is determined from the data as described in Section \ref{se:truncImpulseResp}. This was done on $1000$ realizations of the noise, and depicted in \figref{fig:pdfAndRMSeVStruncTime} by the histogram.
Clearly, the method for selecting the truncation time $t_{\mathrm{trunc}}$ has a good overall performance, based on the mode of its distribution. A closely grouped set of values for $t_{\mathrm{trunc}}$ is obtained around the $90^{\text{th}}$ sample, without significant outliers.

### 2016-02-11 ch05-initvals/InitialValuesPaper.tex
Some minor fixes in captions etc.

\subsection{Stress test of the smoothers}
To test the effectiveness of the initial estimates obtained from these particular smoothers, an extra set of $n_{\mathrm{MC}} = 100$ Monte Carlo simulations were performed.
In particular, all combinations of
\begin{itemize}
  \item low-pass, high-pass, band-pass and band-stop 
  \item Chebyshev Type I, Chebyshev Type II, Elliptical and Butterworth
\end{itemize}
discrete-time filters (see \figref{fig:bodeplots} and \tabref{tbl:init:stresstest}) of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} are simulated.
Each of these filters $\true{G}$ has been normalized such that $\norm[2]{\true{G}} = 1$.
The low-pass and high-pass filtes have a cross-over frequency of $\frac{\pi}{2} \unit{rad/S}$. 
The band-pass, respectively band-stop, filters have a passband, respectively stopband, in the frequency range$\left[ \frac{2\pi}{5}, \frac{3\pi}{5}\right] \unit{rad/S}$.
Note also that both the band-pass and band-stop filters have a McMillan degree of 20 as per the \MATLAB conventions.

>>>>

\subsection{Stress test of the smoothers}
To test the effectiveness of the initial estimates obtained from these particular smoothers, an extra set of $n_{\mathrm{MC}} = 100$ Monte Carlo simulations were performed.
In particular, all combinations of
\begin{itemize}
  \item low-pass, high-pass, band-pass and band-stop 
  \item Chebyshev Type I, Chebyshev Type II, Elliptical and Butterworth
\end{itemize}
discrete-time filters~\citep{Zverev1967} of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} are simulated.
Each of these filters $\true{G}$ has been normalized such that $\norm[2]{\true{G}} = 1$.
The low-pass and high-pass filtes have a cross-over frequency of $\frac{\pi}{2} \unit{rad/S}$. 
The band-pass, respectively band-stop, filters have a passband, respectively stopband, in the frequency range$\left[ \frac{2\pi}{5}, \frac{3\pi}{5}\right] \unit{rad/S}$.
Note also that both the band-pass and band-stop filters have a McMillan degree of 20 as per the \MATLAB conventions.
See \tabref{tbl:init:stresstest} for an overview of the filters and  \figref{fig:bodeplots} for the corresponding bode plots.
